EDA

### 2019-08-27 paper_results/EDA/eda.Rmd
Updated readme

---
title: "EDA"
author: "The Competent Ones"
date: "August 4, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r libraries}
library(devtools)
library(deuce)
library(knitr)
#devtools::load_all("..") # Loads courtsports package
```

>>>>

---
title: "EDA"
author: ""
date: "Sept. 5, 2019"
output: 
  html_document:
    toc:  true
    toc_float:  true
    code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(message = FALSE)
knitr::opts_chunk$set(warning = FALSE)

```{r libraries}
library(devtools)
library(deuce)
library(knitr)
#library(courtsports) ## UNCOMMENT if running
#devtools::load_all("..") # Loads courtsports package
